Validation of Visual Statistical Inference, Applied to Linear Models

### 2013-04-12 paper_jasa.tex
finished with conclusions

The lineup protocol operates analogously to statistical tests that have broad alternative hypotheses. If the null hypothesis is rejected, generally we can say that ``there is something there'' but not specifically what it is in the data that triggers the rejection. Follow-up questions on the reasons provide qualitative insight. Multiple comparisons are often done to refine and understand the results of the general conventional testing, and perhaps some similar approaches might be developed for visual inference.

@@

Lineups have been successfully applied to evaluate the power of competing graphical designs \citep{heike:2012}, and to detecting signal presence in large $p$, small $n$ data \citep{niladri:2012}. It is hoped that this proves to be  valuable in data mining applications, and exploratory analyses, where there are no existing gauges of statistical significance.

>>>>

The lineup protocol operates similarly to statistical tests that have broad alternative hypotheses. If the null hypothesis is rejected, generally we can say that ``there is something there'' but not specifically what it is in the data that triggers the rejection. Follow-up questions on the reasons provide qualitative insight. In conventional testing, multiple comparisons are often done to refine and understand the test results, and perhaps some similar approaches might be developed for visual inference.

@@

Visual inference has been successfully used in two practical applications: to evaluate the power of competing graphical designs \citep{heike:2012}, and to detecting signal presence in large $p$, small $n$ data \citep{niladri:2012}. It is hoped that the lineup protocol will prove to be  valuable in data mining applications, and exploratory analyses, where there are no existing gauges of statistical significance.
